Capstone Movielens Report

### 2025-11-25 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function description: get_fine_tune.param.endpoints.

#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
\

>>>>

#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L109) Function {#func.get_fine_tune.param.endpoints}
\
